Inference methods comparison for the simplified Naomi model

### 2023-02-07 src/naomi-simple_compare/comparison.Rmd
Fixes, tabbed histogram ECDF plots, tabbed KS plots

```{r}
unique(names(tmb$fit$obj$env$par))
```

@@

```{r}
data.frame(
  "TMB" = tmb$time,
  "aghq" = aghq$time,
  "tmbstan" = tmbstan$time
)
```

# Histogram

```{r}
histogram_plot("beta_rho", i = 1)
histogram_plot("beta_anc_rho")
```

# KS

## Individual parameters

```{r}
ks_helper <- function(par) to_ks_df(par) %>% ks_plot(par = par)

ks_helper("beta")
ks_helper("logit")
ks_helper("log_sigma")

ks_helper("u_rho_x")
ks_helper("u_rho_xs")
ks_helper("us_rho_x")
ks_helper("us_rho_xs")
ks_helper("u_rho_a")
ks_helper("u_rho_as")

ks_helper("u_alpha_x")
ks_helper("u_alpha_xs")
ks_helper("us_alpha_x")
ks_helper("us_alpha_xs")
ks_helper("u_alpha_a")
ks_helper("u_alpha_as")
ks_helper("u_alpha_xa")

ks_helper("ui_anc_rho_x")
ks_helper("ui_anc_alpha_x")
ks_helper("log_or_gamma")
```

@@

```{r}
ks_summary <- lapply(unique(names(tmb$fit$obj$env$par)), function(x) {
  to_ks_df(x) %>%
    group_by(method) %>%
    summarise(ks = mean(ks), par = x)
}) %>%
  bind_rows() %>%
  pivot_wider(names_from = "method", values_from = "ks") %>%
  rename(
    "Parameter" = "par",
    "KS(aghq, tmbstan)" = "aghq",
    "KS(TMB, tmbstan)" = "TMB",
  )

@@

Let's look into this further by plotting the histograms:

```{r}
lapply(big_ks, histogram_plot)
```

>>>>

```{r}
pars <- unique(names(tmb$fit$obj$env$par))
```

@@

```{r}
data.frame(
  "TMB" = tmb$time,
  "aghq" = aghq$time,
  "adam" = adam$time,
  "tmbstan" = tmbstan$time
)

adam <- adam$adam
```

# Histograms {.tabset .tabset-fade}

```{r}
beta_rho <- histogram_and_ecdf("beta_rho", i = 1, return_df = TRUE)
saveRDS(beta_rho$df, "beta_rho.rds")
```

## `beta`

```{r}
lapply(pars[stringr::str_starts(pars, "beta")], histogram_and_ecdf)
```

## `logit`

```{r}
lapply(pars[stringr::str_starts(pars, "logit")], histogram_and_ecdf)
```

## `log_sigma`

```{r}
lapply(pars[stringr::str_starts(pars, "log_sigma")], histogram_and_ecdf)
```

# KS plots

## Individual parameters {.tabset .tabset-fade}

```{r}
ks_helper <- function(par, ...) {
  to_ks_df(par) %>% ks_plot(par, ...)
}
```

### `beta`

```{r}
ks_helper("beta")
ks_helper("beta", method1 = "TMB", method2 = "adam")
```

### `logit`

```{r}
ks_helper("logit")
ks_helper("logit", method1 = "TMB", method2 = "adam")
```

### `log_sigma`

```{r}
ks_helper("log_sigma")
ks_helper("log_sigma", method1 = "TMB", method2 = "adam")
```

### `u_rho_x`

```{r}
ks_helper("u_rho_x")
ks_helper("u_rho_x", method1 = "TMB", method2 = "adam")
```

### `u_rho_xs`

```{r}
ks_helper("u_rho_xs")
ks_helper("u_rho_xs", method1 = "TMB", method2 = "adam")
```

### `us_rho_x`

```{r}
ks_helper("us_rho_x")
ks_helper("us_rho_x", method1 = "TMB", method2 = "adam")
```

### `us_rho_xs`

```{r}
ks_helper("us_rho_xs")
ks_helper("us_rho_xs", method1 = "TMB", method2 = "adam")
```

### `u_rho_a`

```{r}
ks_helper("u_rho_a")
ks_helper("u_rho_a", method1 = "TMB", method2 = "adam")
```

### `u_rho_as`

```{r}
ks_helper("u_rho_as")
ks_helper("u_rho_as", method1 = "TMB", method2 = "adam")
```

### `u_alpha_x`

```{r}
ks_helper("u_alpha_x")
ks_helper("u_alpha_x", method1 = "TMB", method2 = "adam")
```

### `u_alpha_xs`

```{r}
ks_helper("u_alpha_xs")
ks_helper("u_alpha_xs", method1 = "TMB", method2 = "adam")
```

### `us_alpha_x`

```{r}
ks_helper("us_alpha_x")
ks_helper("us_alpha_x", method1 = "TMB", method2 = "adam")
```

### `us_alpha_xs`

```{r}
ks_helper("us_alpha_xs")
ks_helper("us_alpha_xs", method1 = "TMB", method2 = "adam")
```

### `u_alpha_a`

```{r}
ks_helper("u_alpha_a")
ks_helper("u_alpha_a", method1 = "TMB", method2 = "adam")
```

### `u_alpha_as`

```{r}
ks_helper("u_alpha_as")
ks_helper("u_alpha_as", method1 = "TMB", method2 = "adam")
```

### `u_alpha_xa`

```{r}
ks_helper("u_alpha_xa")
ks_helper("u_alpha_xa", method1 = "TMB", method2 = "adam")
```

### `ui_anc_rho_x`

```{r}
ks_helper("ui_anc_rho_x")
ks_helper("ui_anc_rho_x", method1 = "TMB", method2 = "adam")
```

### `ui_anc_alpha_x`

```{r}
ks_helper("ui_anc_alpha_x")
ks_helper("ui_anc_alpha_x", method1 = "TMB", method2 = "adam")
```

### `log_or_gamma`

```{r}
ks_helper("log_or_gamma")
ks_helper("log_or_gamma", method1 = "TMB", method2 = "adam")
```

@@

```{r}
ks_summary <- lapply(unique(names(tmb$fit$obj$env$par)), function(x) {
  to_ks_df(x) %>%
    group_by(method) %>%
    summarise(ks = mean(ks), par = x)
}) %>%
  bind_rows() %>%
  pivot_wider(names_from = "method", values_from = "ks") %>%
  rename(
    "Parameter" = "par",
    "KS(adam, tmbstan)" = "adam",
    "KS(aghq, tmbstan)" = "aghq",
    "KS(TMB, tmbstan)" = "TMB",
  )

@@
